A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2023-07-21 paper/fascd.tex
update, and minor clean, of adv-diff example 8.3
no change in parallel iterations after halo exchange
FASCD bug fix

\begin{example}  \label{ex:results:advdiff}
We consider the advection-diffusion VI problem in Example \ref{ex:advectiondiffusion}.  Let $\Omega=(-1,1)^d$ for $d=2,3$, the diffusivity $\eps=0.1$ (equation \eqref{eq:advectiondiffusionstrong}), and we impose zero Dirichlet boundary conditions.  The 2D problem satisfied the coercivity hypothesis with a divergence-free velocity field $\bX = (7+5y,-5x)$, but in 3D, for variety's sake, we set $\bX = (7+5y,-5x,2z)$ so $\grad\cdot\bX \ne 0$.  The discontinuous source term $\phi \in L^\infty(\Omega)$ satisfied $\phi\ge 0$ in half of the domain, with positive circular patches, while values were negative in the other half; details are in the associated code.   While the other Examples in this Section are unilateral, here the solution was box-constrained: $0 \le u \le 1$.  Figure \ref{fig:results:advdiff} shows coincidence sets for the 2D problem; the 3D sets are comparable in regularity and general pattern.

@@

To minimally-resolve the coincidence set we used a coarse mesh with $m_0=16^d$ vertices.  The 2D solver applied $P_1$ elements and a single processor, but in 3D we used $Q_1$ elements (hexahedra) and $P=16$ processes.  The smoother was two (fixed) RS Newton iterations,  with three preconditioned GMRES iterations to approximately solve the arising linear systems.  The additive Schwarz method (ASM) preconditioner applied incomplete factorization (ILU) preconditioning on each core.  The coarse solver was RS Newton and LU, iterated to convergence.  Tolerances \id{rtol} $=10^{-5}$ and \id{atol} $=10^{-9}$ were used in \eqref{eq:stoppingcriterion}.

F-cycle iteration results are shown in Table \ref{tab:results:advdiff}.  Despite the hint of growing iterations under mesh refinement, a few iterations sufficed up to memory-limited resolutions.  For any of the higher resolution runs, the FASCD F-cycle solver took less time than generating the $P_1$ mesh hierarchy.  The local Péclet number $\text{Pe}=\|\bX(x,y,z)\|_2 L \eps^{-1}$, with $L=2$ the width of $\Omega$, varied from 40 to 260; the mesh Péclet number $m_J^{-1/d}\,\text{Pe}$ varied accordingly.  Thus the $m_J\le 121^d$ problems were advection-dominated while those with $m_J\ge 481^d$ were diffusion-dominated, but the smoother was the same in all cases, and the iterations were nearly constant.
\end{example}

>>>>

\begin{example}  \label{ex:results:advdiff}
Consider the advection-diffusion VI problem in Example \ref{ex:advectiondiffusion} with $\Omega=(-1,1)^d$, $d=2,3$, diffusivity $\eps=0.1$ in equation \eqref{eq:advectiondiffusionstrong}, and zero Dirichlet boundary conditions.  We made the 2D problem satisfy the coercivity hypothesis with a divergence-free velocity field $\bX = (7+5y,-5x)$, but in 3D, for variety's sake, we set $\bX = (7+5y,-5x,2z)$ so $\grad\cdot\bX \ne 0$.  The chosen discontinuous source term $\phi \in L^\infty(\Omega)$ satisfies $\phi\ge 0$ in half of the domain, with positive circular patches, with negative values in the other half; details are in the associated code.  While the other Examples in this Section are unilateral, here the solution is box-constrained: $0 \le u \le 1$.  Figure \ref{fig:results:advdiff} shows coincidence sets for the 2D problem; the 3D sets are comparable in regularity and general pattern.

@@

The 2D solver applied $P_1$ elements and a single processor, but in 3D the elements were chosen to be $Q_1$ (hexahedra) and the run parallel ($P=16$ processes).  A coarse mesh with $m_0=16^d$ vertices minimally-resolved the coincidence set.  The smoother was two (fixed) RS Newton iterations, with three preconditioned GMRES iterations to approximately solve the arising linear systems; the preconditioning was additive Schwarz method (ASM) with incomplete factorization (ILU) on each process.  The coarse solver was RS Newton and LU, iterated to convergence.  Tolerances \id{rtol} $=10^{-5}$ and \id{atol} $=10^{-9}$ were used in \eqref{eq:stoppingcriterion}.

F-cycle iteration results are shown in Table \ref{tab:results:advdiff}.  Despite the hint of growing iterations under mesh refinement, a few iterations sufficed up to memory-limited resolutions.  For any of the higher resolution runs, the FASCD F-cycle solver took less time than generating the mesh hierarchy.  The local Péclet number $\text{Pe}=\|\bX(x,y,z)\|_2 L \eps^{-1}$, with $L=2$ the width of $\Omega$, varied from 40 to 260.  The mesh Péclet number $m_J^{-1/d}\,\text{Pe}$ varied accordingly, and though the $m_J\le 121^d$ problems were advection-dominated, those with $m_J\ge 481^d$ were diffusion-dominated, and the smoother was the same in all cases, with nearly-constant iterations.
\end{example}
